Bias variance trade-off comparison of regression models

### 2022-11-30 doc/paper.tex
fix overfit conclusion

Looking at a completely different way of performing our regression, the decision tree model provides interesting results. Looking at (Fig.~\ref{tree}), the bias variance trade-off is much different, as the variance increases much more and the bias decreases less. This yields a higher bias and variance, and since the MSE can be expressed as the sum of both these factors, this provides a larger test mean squared error. The decision tree regressor yields an MSE of 0.0077, over double that of our best result using ridge regression. Though it does not appear to overfit our training data, the decision tree does not provide impressive results for our regression case. The fact that decision trees are very explainable does not provide a useful argument for selecting the decision tree model, as we are dealing with conditions based on numbers which yield little intuition.

@@

\subsection{Conclusion}
Ridge proved to be the best regression model, as the regularization allows us to drive down the MSE to an impressive 0.0031 whilst delaying the overfitting. Ridge was able to mentain a low bias and variance, an impressive 14\% decrease from OLS' results. Decision trees didn't overfit, but was unable to beat the MSE of ridge and OLS as the bias variance trade-off featured both a higher bias and variance. The FFNN required a great increase in computational cost whilst not being able to beat the MSE of OLS and Ridge. For 5 hidden layers, the FFNN yields a lower MSE than the decision tree.

>>>>

Looking at a completely different way of performing our regression, the decision tree model provides interesting results. Looking at (Fig.~\ref{tree}), the bias variance trade-off is much different, as the variance increases much more and the bias decreases less. This yields a higher bias and variance, and since the MSE can be expressed as the sum of both these factors, this provides a larger test mean squared error. The decision tree regressor yields an MSE of 0.0077, over double that of our best result using ridge regression. The decision tree seems to overfit almost immediately as the variance increases, and does thus not provide impressive results for our regression case. The fact that decision trees are very explainable does not provide a useful argument for selecting the decision tree model, as we are dealing with conditions based on numbers which yield little intuition.

@@

\subsection{Conclusion}
Ridge proved to be the best regression model, as the regularization allows us to drive down the MSE to an impressive 0.0031 whilst delaying the overfitting. Ridge was able to mentain a low bias and variance, an impressive 14\% decrease from OLS' results. Decision trees overfit, and were unable to beat the MSE of ridge and OLS as the bias variance trade-off featured both a higher bias and variance. The FFNN required a great increase in computational cost whilst not being able to beat the MSE of OLS and Ridge. For 5 hidden layers, the FFNN yields a lower MSE than the decision tree.
